\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{enumerate}

\begin{document}

\ul{The following section only involves calculation and some analytical explanation which requires some background reading. You may use the list references given. }\\

\textbf{5.5}   Show how you would determine the inductance value so that a current ripple magnitude in the lamp is less than 15\% of its rated value, at chopping frequency of 15 kHz. \emph{(Include any comments to support your answer)}

\begin{center}
\begin{flushleft} Because: \end{flushleft}
 
$$\Delta i = (1-k)\frac{T_p*V_o}{L}$$\\
\begin{flushleft} Where, \end{flushleft}
$$i = V_o / R_L$$\\
\begin{flushleft} Thus we can have, \end{flushleft}
\begin{eqnarray*}
\frac{\Delta i}{i} &=& \frac{(1-k)\frac{T_p*V_o}{L}}{\frac{V_o}{R_L}}\\
\frac{\Delta i}{i} &=& (1-k)*\frac{T_p*R_L}{L}\\
\frac{\Delta i}{i} &=& (1-k)*\frac{R_L}{L*F}
\end{eqnarray*}
\begin{flushleft} Thus, \end{flushleft}\begin{equation} \label{eq:solve}
L = (1-k)*\frac{R_L}{F*\frac{\Delta i}{i}}\end{equation}

And We have: $F = 15khz$, $\frac{\Delta i}{i}=15\%$, $k=0.25$. Knowing the R value, we then can calculate the L value.


\end{center}

\textbf{5.6} On the basis of the derived relationship between the inductance and the frequency, state: 
\begin{enumerate}[(a)]
\item how the chopping frequency affects the size of the filtering inductor for a give average current;  \\

As we can see from the formula \ref{eq:solve}, That when keeping $\frac{\Delta i}{i}$ and $k$ as a constant,  The higher the F the lower the L. Thus, at a certain degree, increasing the chopping frequency will help decreasing the size the inductor.
\item what causes the limitation on the switching frequency.\\

First, the semi-conductor itself won't allow the chopping frequency to increase without limitation. And this true especially because we are right now dealing with the power electronics .\\
Second, the switching losses is not neglectible. There are power losses along with each switching.
\end{enumerate}


 

\end{document}
